An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-28 4_method.tex
reformalize beading B=(W,L) and site J => S

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads and a diameter $d = 2R(v)$  as:
\begin{align*}
    %B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
    w_i &= 2R(v) / n  & \text{for all $i \leq n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i \leq n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
Now that each node has been assigned a beading we proceed to generate the sites along its support edge which define the toolpath.
For each upward half-edge \jun{half-edge?} $\overrightarrow{v_0 v_1}$ we decide the location ($v$), width ($w$) of the $i$-th site $J$ based on the beading $B = B^{v_1}$:
\begin{align*}
J &= \{ v, w, i \} \\ 
v &= v_1 + (v_0 - v_1) \frac{R(v_1) - l_i^B}{R(v_1) - R(v_0)} \\ 
w &= w_i^B
% \\ i^J &= i
\end{align*}
for any $i$ for which $R(v_0) < l_i^B \leq R(v_1)$.
See \cref{site_placement}.
We store all sites of an edge in a mapping from edge to a list of sites.

@@

Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
Such intersections cause overfill because the nozzle passes the location multiple times.
We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
In order to retreat a polyline which ends in a site $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.
See \cref{polyline_reduction}.

>>>>

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads and a diameter $d = 2R(v)$  as:
\begin{align*}
%    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
    B(n,d) &= \left( W(n,d), L(n,d) \right)\\
    W(n,d) &= \left\{  w_0 , \dots, w_{n-1} \right\} \\
    L(n,d) &= \left\{ l_0 , \dots, l_{n-1} \right\} \\
    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i <t n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
Now that each node has been assigned a beading we proceed to generate the toolpath sites along the edges of the ST.
A site $S$ consists of a location $v$ a width $w$ and an index $i$, which are computed for an edge $v_0v_1$ from the beading $B$ of the upper node $v_1$:
\begin{align*}
S &= \{ v, w, i \} \\ 
v &= v_1 + (v_0 - v_1) \frac{R(v_1) - l_i^B}{R(v_1) - R(v_0)} \\ 
w &= w_i^B
% \\ i^S &= i
\end{align*}
for any $i$ for which $R(v_0) < l_i^B \leq R(v_1)$.
See \cref{site_placement}.
We store all sites of an edge in a mapping from edge to a list of sites.

@@

Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
Such intersections cause overfill because the nozzle passes the location multiple times.
We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.
See \cref{polyline_reduction}.

### 2019-08-28 5_generalization.tex
reformalize beading B=(W,L) and site J => S

\begin{definition}\label{beading_scheme_definition}
The beading scheme is configured by the following set of parameters and functions:
$$
\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\},
$$
where, as introduced in previous section, $\alpha_{\text{max}}$ is the limit bisector angle,
$q(d)$ the quantization operator,
$t(n)$ the transition length
and
$t_0(n)$ the transition anchor position. \jun{check whether this last one has been defined.}
$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
\end{enumerate}

@@

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d_\text{max}^\text{unmarked} &= w^* \\ 
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w^* \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
t(n) &= w^* \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
The toolpath locations $L$ ensure that beads are extruded from the center of where they end up, that the beads don't overlap and that the symmetry restrictions are met.

@@

\paragraph{Inward distributed scheme}
\todo{TODO: merge general distributed with inward distributed decsription.}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w^* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
%\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
See \cref{formula_inward_distributed}.

>>>>

\begin{definition}\label{beading_scheme_definition}
The beading scheme is configured by the following set of parameters and functions:
$$
\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), B(n, d) \right\},
$$
where, as introduced in previous section, $\alpha_{\text{max}}$ is the limit bisector angle,
$q(d)$ the quantization operator,
$t(n)$ the transition length
and
$t_0(n)$ the transition anchor position \jun{check whether this last one has been defined.}
and
$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$.
%$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $B$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is positive, monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
\end{enumerate}

@@

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
\begin{array}{rlrl}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}    &    t_\text{beading} &= w^* \\
d_\text{max}^\text{unmarked} &= w^*    &    t(n) &= w^*  \\ 
d^\text{discretization} &= \SI{0.2}{\milli\meter}    &    t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent}     &     \alpha_\text{max} &= \SI{135}{\degree} \\
\end{array} \\
%\end{align*}
%\begin{align*}
L(n,d)_i = 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures thatwe don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
The toolpath locations $L$ ensure 
that the beads don't overlap,
that beads are extruded from the center of where they end up
and that the symmetry restrictions are met.

@@

\paragraph{Inward distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w^* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
%\paragraph{Inward distributed}
For example, we can choose an $M$ which distributes the discrepancy over the innermost beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
%Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
See \cref{formula_inward_distributed}.

### 2019-08-28 6_validation.tex
reformalize beading B=(W,L) and site J => S

From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.

>>>>

From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2 \times 10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.
